Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-07-09 manuscript/appB.Rmd
switches order of up and lo BCI to lo then up for tables

```{r agg_fxn, echo=FALSE, message=FALSE, warning=FALSE}
agg_fxn <- function(mcmc_frame){
  out <- ddply(mcmc_frame, .(Parameter), summarise,
               mean_value = mean(value),
               sd_value = sd(value),
               up_BCI = quantile(value, 0.975),
               lo_BCI = quantile(value, 0.025))
  return(out)
}
spp_list <- c("BOGR", "HECO", "PASM", "POSE")
spp_name <- c("B. gracilis.", "H. comata.", "P. smithii.", "P. secunda.")
```

>>>>

```{r agg_fxn, echo=FALSE, message=FALSE, warning=FALSE}
agg_fxn <- function(mcmc_frame){
  out <- ddply(mcmc_frame, .(Parameter), summarise,
               mean_value = mean(value),
               sd_value = sd(value),
               lo_BCI = quantile(value, 0.025),
               up_BCI = quantile(value, 0.975))
  return(out)
}
spp_list <- c("BOGR", "HECO", "PASM", "POSE")
spp_name <- c("B. gracilis.", "H. comata.", "P. smithii.", "P. secunda.")
```
